\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-03-21 write_up/mixfishsim_ecolmod.tex
Removing guidance text

\begin{abstract}
\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
should state briefly the purpose of the research, the principal results and
major conclusions. An abstract is often pnresented separately from the article,
so it must be able to stand alone. For this reason, References should be
avoided, but if essential, then cite the author(s) and year(s). Also,
non-standard or uncommon abbreviations should be avoided, but if essential they
must be defined at their first mention in the abstract itself.  Graphical
abstract: Although a graphical abstract is optional, its use is encouraged as
it draws more attention to the online article. The graphical abstract should
summarize the contents of the article in a concise, pictorial form designed to
capture the attention of a wide readership. Graphical abstracts should be
submitted as a separate file in the online submission system. Image size:
Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
proportionally more. The image should be readable at a size of 5 x 13 cm using
a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
MS Office files.] \\}

Fishing exploits spatially and temporally hetergenous fish populations, using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

@@

\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
adequate background, avoiding a detailed literature survey or a summary of the
results.] \\}

Fishers exploit fish populations that are heterogenously distributed in space
and time with verying knowledge of species distributions using
species-unselective fishing gear. Fisheries that catch an assemblage of
species, known as mixed fisheries, when managed by single-species quotas can
end up discarding overquota catch leading to overexploitation of fish
populations. Reducing discarding is crucial to ensure biological and economic
sustainability of fisheries and implementation of an ecosystem approach to
fisheries. As such there is increasing interest in technical solutions such as
gear and spatial closures as ways of avoiding discards.  \\

@@

\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
reproduced by an independent researcher. Methods that are already published
should be summarized, and indicated by a reference.  If quoting directly from a
previously published method, use quotation marks and also cite the source. Any
modifications to existing methods should also be described.] \\ }

We develop a simulation model with a modular event-based approach, where
modules are implemented on independent time-scales appropriate to capture the
characteristic of the process modelled (Figure 1). The fishing model operated on a
tow-by-tow basis, while population dynamics (fishing and natural mortality,
growth) operate on a daily time-step.  Population movement occurs on a
weekly time-step, while recruitment occurs periodcally each year for a set
time period (e.g. 3 weeks) at at specified point individual to a species. The
simulation framework is implemented in the statistical software package R
\cite{RCoreTeam2017}; available as an R package from the authors github
(\url{www.github.com/pdolder/MixFishSim}).\\

@@

\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
repeat, the background to the article already dealt with in the	Introduction
and lay the foundation for further work.  In contrast, a
\underline{Calculation} section represents a practical development from a
theoretical basis.] \\}

\subsection{Population parameterisation}

@@

\textcolor{gray}{[Guidance: Results should be clear and concise.]}

@@

\textcolor{gray}{[Guidance: This should explore the significance of the results 
of the work, not repeat them. A combined Results and Discussion section is
often appropriate.  Avoid extensive citations and discussion of published
literature.]}

\section{Conclusions}

\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
in a short Conclusions section, which may stand alone or form a subsection of a
Discussion or Results and Discussion section.]}

\section*{Appendices}

\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
be identified as A, B, etc.  Formulae and equations in appendices should be
given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
Fig. A.1, etc.]}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

>>>>

\begin{abstract}
%\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
%should state briefly the purpose of the research, the principal results and
%major conclusions. An abstract is often pnresented separately from the article,
%so it must be able to stand alone. For this reason, References should be
%avoided, but if essential, then cite the author(s) and year(s). Also,
%non-standard or uncommon abbreviations should be avoided, but if essential they
%must be defined at their first mention in the abstract itself.  Graphical
%abstract: Although a graphical abstract is optional, its use is encouraged as
%it draws more attention to the online article. The graphical abstract should
%summarize the contents of the article in a concise, pictorial form designed to
%capture the attention of a wide readership. Graphical abstracts should be
%submitted as a separate file in the online submission system. Image size:
%Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
%proportionally more. The image should be readable at a size of 5 x 13 cm using
%a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
%MS Office files.] \\}
%
Fishing exploits spatially and temporally hetergenous fish populations, using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

@@

%\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
%adequate background, avoiding a detailed literature survey or a summary of the
%results.] \\}
%
Fishers exploit fish populations that are heterogenously distributed in space
and time with verying knowledge of species distributions using
species-unselective fishing gear. Fisheries that catch an assemblage of
species, known as mixed fisheries, when managed by single-species quotas can
end up discarding overquota catch leading to overexploitation of fish
populations. Reducing discarding is crucial to ensure biological and economic
sustainability of fisheries and implementation of an ecosystem approach to
fisheries. As such there is increasing interest in technical solutions such as
gear and spatial closures as ways of avoiding discards.  \\

@@

%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
%reproduced by an independent researcher. Methods that are already published
%should be summarized, and indicated by a reference.  If quoting directly from a
%previously published method, use quotation marks and also cite the source. Any
%modifications to existing methods should also be described.] \\ }
%
We develop a simulation model with a modular event-based approach, where
modules are implemented on independent time-scales appropriate to capture the
characteristic of the process modelled (Figure 1). The fishing model operated on a
tow-by-tow basis, while population dynamics (fishing and natural mortality,
growth) operate on a daily time-step.  Population movement occurs on a
weekly time-step, while recruitment occurs periodcally each year for a set
time period (e.g. 3 weeks) at at specified point individual to a species. The
simulation framework is implemented in the statistical software package R
\cite{RCoreTeam2017}; available as an R package from the authors github
(\url{www.github.com/pdolder/MixFishSim}).\\

@@

%\textcolor{gray}{[Guidance: A \underline{Theory} section should extend, not
%repeat, the background to the article already dealt with in the	Introduction
%and lay the foundation for further work.  In contrast, a
%\underline{Calculation} section represents a practical development from a
%theoretical basis.] \\}
%
\subsection{Population parameterisation}

@@

%\textcolor{gray}{[Guidance: Results should be clear and concise.]}

@@

%\textcolor{gray}{[Guidance: This should explore the significance of the results 
%of the work, not repeat them. A combined Results and Discussion section is
%often appropriate.  Avoid extensive citations and discussion of published
%literature.]}
%
\section{Conclusions}

%\textcolor{gray}{[Guidance: The main conclusions of the study may be presented 
%in a short Conclusions section, which may stand alone or form a subsection of a
%Discussion or Results and Discussion section.]}
%
\section*{Appendices}

%\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
%be identified as A, B, etc.  Formulae and equations in appendices should be
%given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
%appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
%Fig. A.1, etc.]}
%
\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}
